An open and continuously updated fern tree of life (FTOL)

### 2022-01-30 ms/manuscript.Rmd
Update MS

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(targets)
library(assertr)
library(ape)
library(scales)
library(tidyverse)
library(rgnparser)
library(glue)
library(phytools)

@@

backbone_tree_full <- 
	plastome_tree %>%
	ape::root.phylo("Anthoceros_angustus") %>%
	ape::ladderize() %>%
	ape::drop.tip(og_taxa)

family_exemp <-
tibble(
	species = backbone_tree_full$tip.label
) %>%
	mutate(genus = str_split(species, "_") %>% map_chr(1)) %>%
	left_join(select(ppgi_taxonomy, family, genus), by = "genus") %>%
	group_by(family) %>%
	slice(1) %>%
	ungroup() %>%
	pull(species)

backbone_tree_exemp <- ape::keep.tip(backbone_tree_full, family_exemp)

bb_trans_table <-
	tibble(species = backbone_tree_exemp$tip.label) %>%
	mutate(genus = str_split(species, "_") %>% map_chr(1)) %>%
	left_join(select(ppgi_taxonomy, family, genus), by = "genus") %>%
	left_join(accepted_sampling_by_rank, by = c(family = "name")) %>%
	assert(not_na, species, family, n) %>%
	select(tip.label = species, clade.label = family, N = n) %>%
	## set crown node depth to 1/2 the maximum depth
	mutate(
		depth = sapply(backbone_tree_exemp$tip.label, function(x,y) 
	0.5*y$edge.length[which(backbone_tree_exemp$edge[,2] ==
	which(y$tip.label == x))], y = backbone_tree_exemp)
	)

## convert
tt <- phylo.toBackbone(backbone_tree_exemp, bb_trans_table)
## plot
plot(tt)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(rmarkdown)
library(bookdown)
library(targets)
library(assertr)
library(ape)
library(scales)
library(tidyverse)
library(rgnparser)
library(glue)

@@

family_exemp <-
tibble(species = plastome_tree$tip.label) %>%
	mutate(
		genus = str_split(species, "_") %>% map_chr(1),
		phy_order = seq_len(nrow(.))) %>%
	left_join(select(ppgi_taxonomy, family, genus), by = "genus") %>%
	mutate(family = replace_na(family, "og")) %>%
	group_by(family) %>%
	slice(1) %>%
	ungroup() %>%
	arrange(phy_order)

backbone_tree <- ape::keep.tip(plastome_tree, family_exemp$species)
backbone_tree$tip.label <- family_exemp$family

backbone_tree$node.label <- str_replace(backbone_tree$node.label, "100", "")

backbone_tree <-
	backbone_tree %>%
	root.phylo("og") %>%
	ladderize() %>%
	drop.tip("og")

plot(backbone_tree, font = 1)
nodelabels(backbone_tree$node.label, frame = "none", col = "grey", cex = 0.8)
```
